I am writing to apply for the position of Software Architect.

My name is Pedro Moreira and I am currently a Senior Software Engineer at OMP, a leading supply chain software company.

Your job posting drew my attention because it matches my dream job exactly. I love analyzing complex challenges related with distributed systems and design highly scalable solutions.

I have strong technical skills and I am not afraid to take on new challenges. My skills combined with my experience and relentless attention to detail have allowed me to design and deliver high quality distributed systems throughout my career. I am capable of doing high level conceptual analysis and engage in collaborative discussions as well as low level debugging on my own. I am comfortable with modern technologies such as AWS, Terraform and Kubernetes, to name a few, and I can easily learn new ones if my work requires it.

I am a valued team member whom colleagues enjoy working with, as I actively mentor and contribute to the team, earning consistent positive feedback throughout the years:

\emph{"I was genuinely impressed with your analysis (...). I've read the materials you started from and did not imagine they could be distilled into the clear list of requirements you presented."}

\emph{"To me, our collaboration and communication is honest, constructive, and respectful. You have a down-to-earth and pragmatic mentality and use that to challenge others."}

\emph{"You work very detailed and straight to the point. All you create has a very high quality and you thought well about it beforehand."}

Thank you for considering my application. I believe I am a good fit for this position and I look forward to discuss how my skills match up with what you're looking for.
